---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# riot

<!-- badges: start -->
[![R-CMD-check](https://github.com/astamm/riot/workflows/R-CMD-check/badge.svg)](https://github.com/astamm/riot/actions)
[![test-coverage](https://github.com/astamm/riot/workflows/test-coverage/badge.svg)](https://github.com/astamm/riot/actions)
[![Codecov test coverage](https://codecov.io/gh/astamm/riot/branch/master/graph/badge.svg)](https://app.codecov.io/gh/astamm/riot?branch=master)
[![pkgdown](https://github.com/astamm/riot/workflows/pkgdown/badge.svg)](https://github.com/astamm/riot/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/riot)](https://CRAN.R-project.org/package=riot)
<!-- badges: end -->

The goal of `riot` is to provide readers and writers from and to standard file
formats (`.vtk`, `.vtp` and `.fds`) that store diffusion MRI tractography data.

## Installation

You can install the development version of
[`riot`](https://astamm.github.io/riot/) from [GitHub](https://github.com/)
with:

``` r
# install.packages("devtools")
devtools::install_github("astamm/riot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(riot)
uf_left  <- read_fascicles(system.file("extdata", "UF_left.vtp",  package = "riot"))
uf_left
```

## Dependencies

The [`riot`](https://astamm.github.io/riot/) package has two dependencies: [VTK](https://vtk.org/) and [TinyXML-2](https://github.com/leethomason/tinyxml2). They both have been slightly altered with respect to the original softwares.
Specifically, `vtk/include/utf8.h` header file has been modified to ensure LF line endings. Also, `tinyxml2.cpp` has been modified to avoid the use of `stdout` and `printf` as per *Writing R Extensions* manual recommendations because `R` has its own input/output mechanism for writing to the console.
